---
title: "Anscombe's quartet"
author: "Ronald Rodriguez"
date: "01 de octubre de 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Anscombe's quartet comprises four datasets that have nearly identical simple descriptive 
statistics, yet appear very different when graphed. Each dataset consists of eleven (x,y) points. 
They were constructed in 1973 by the statistician Francis Anscombe to demonstrate 
both the importance of graphing data before analyzing it and the effect of outliers
on statistical properties. He described the article as being intended to counter 
the impression among statisticians that "numerical calculations are exact, but graphs are rough.[1]


```{r libraries,message=FALSE,warning=FALSE}
library("plotly")
library("tidyr")
library("dplyr")
```

## Graphs

```{r anscombe, echo=FALSE}
anscombeData1 <- data.frame(x=c(10.0,8.0,13.0,9.0,11.0,14.0,6.0,4.0,12.0,7.0,5.0),
                           y=c(8.04,6.95,7.58,8.81,8.33,9.96,7.24,4.26,10.84,4.82,5.68))
anscombeData2 <- data.frame(x=c(10.0,8.0,13.0,9.0,11.0,14.0,6.0,4.0,12.0,7.0,5.0),
                            y=c(9.14,8.14,8.74,8.77,9.26,8.10,6.13,3.10,9.13,7.26,4.74))
anscombeData3 <- data.frame(x=c(10.0,8.0,13.0,9.0,11.0,14.0,6.0,4.0,12.0,7.0,5.0),
                            y=c(7.46,6.77,12.74,7.11,7.81,8.84,6.08,5.39,8.15,6.42,5.73))
anscombeData4 <- data.frame(x=c(8.0,8.0,8.0,8.0,8.0,8.0,8.0,19.0,8.0,8.0,8.0),
                            y=c(6.58,5.76,7.71,8.84,8.47,7.04,5.25,12.50,5.56,7.91,6.89))

fit1 <- lm(y ~ x, data = anscombeData1)
fit2 <- lm(y ~ x, data = anscombeData2)
fit3 <- lm(y ~ x, data = anscombeData3)
fit4 <- lm(y ~ x, data = anscombeData4)

p1 <- plot_ly(anscombeData1, x = ~x, y = ~y,type="scatter", mode = 'markers', name = ~"dist1") %>%
  add_lines(x = , y = fitted(fit1),name = ~"reg1")
p2 <- plot_ly(anscombeData2, x = ~x, y = ~y,type="scatter",mode = 'markers') %>%
  add_lines(x = , y = fitted(fit2),name = ~"reg2")
p3 <- plot_ly(anscombeData3, x = ~x, y = ~y,type="scatter",mode = 'markers') %>%
  add_lines(x = , y = fitted(fit3),name = ~"reg3")
p4 <- plot_ly(anscombeData4, x = ~x, y = ~y,type="scatter",mode = 'markers') %>%
  add_lines(x = , y = fitted(fit4),name = ~"reg4")

p <- subplot(p1, p2,p3,p4,nrows=2)
p
```


## References

1- [Anscombe's quartet - https://en.wikipedia.org/wiki/Anscombe%27s_quartet][1] <br>
2- [Frank Anscombe - https://en.wikipedia.org/wiki/Frank_Anscombe][2]


[1]: https://en.wikipedia.org/wiki/Anscombe%27s_quartet
[2]: https://en.wikipedia.org/wiki/Frank_Anscombe